---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# grdash: House Price Indices for Greece

<!-- badges: start -->
<!-- badges: end -->

Get the data from Bank of Greece website, which can be accessed through [here](https://www.bankofgreece.gr/en/statistics/real-estate-market/residential-and-commercial-property-price-indices-and-other-short-term-indices). The file `analysis.R` 
contains the recessary data manipulation in order to bring our data in tidy format.


```{r get prices, message=FALSE, warning=FALSE}
source("analysis.R")
prices <- get_hp()
prices
```

Plot the data according to the base year in order to make meaningfull comparisons.

```{r plot}
prices %>% 
  mutate(base = paste0("Base Year: ", base)) %>% 
  ggplot(aes(date, value, col = name)) +
  geom_line() +
  facet_wrap(~ base, scales = "free_y", labeller = ) +
  theme_bw() +
  labs(
    title = "Index of Prices of Dwellings",
    subtitle = "source: Bank of Greece (BoG)"
  )+
  theme(
    axis.title = element_blank(),
    strip.background = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom"
  )

```

```{r plot-ret}
prices %>% 
  mutate(base = paste0("Base Year: ", base)) %>% 
  group_by(name) %>% 
  mutate(ret = transx::ldiffx(value)*100) %>% 
  ggplot(aes(date, ret, col = name)) +
  geom_line() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_wrap(~ base, scales = "free_y") +
  theme_bw() +
  labs(
    title = "Prices of Dwellings, Quarterly Change",
    subtitle = "source: Bank of Greece (BoG)",
    y = "Change (%)"
  )+
  theme(
    axis.title = element_blank(),
    strip.background = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom"
  )

```


```{r plot-ret-yoy}
prices %>% 
  mutate(base = paste0("Base Year: ", base)) %>% 
  group_by(name) %>% 
  mutate(ret = transx::ldiffx(value, 4)*100) %>% 
  ggplot(aes(date, ret, col = name)) +
  geom_line() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_wrap(~ base, scales = "free_y") +
  theme_bw() +
  labs(
    title = "Prices of Dwellings, Annual Change",
    subtitle = "source: Bank of Greece (BoG)",
    y = "Change (%)"
  )+
  theme(
    axis.title = element_blank(),
    strip.background = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom"
  )

```



## Exuberance analysis

Apply the Phillips et al (2015) GSADF recursive test in order to identify periods
of exuberance.

```{r exuberance}
library(exuber)
rs <- prices %>% 
  select(-base) %>% 
  pivot_wider() %>% 
  drop_na() %>% 
  radf(., lag = 1)
autoplot(rs)

```